\graphicspath{{./figures/}}
\usepackage{pdfpages}
\title{}
\date{}
\begin{document}
\begin{frame}
    \titlepage
\end{frame}

{
\setbeamercolor{background canvas}{bg=blue!40!black,fg=blue!10!white}
\setbeamercolor{normal text}{bg=blue!40!black,fg=blue!10!white}
\setbeamercolor{itemize/enumerate body}{fg=white}
\setbeamercolor{itemize/enumerate subbody}{fg=white}
\setbeamercolor{titlelike}{bg=blue!40!black,fg=blue!10!white}
\begin{frame}<1|handout:1>[noframenumbering]{Changelog}
    \begin{itemize}
    \item 26 April 2021: chroot ls: add first missing chroot command; consistently use /tmp/example
    \item 26 April 2021: mount namespaces API: add mount commands that would be needed to actually run ls
    \item 26 April 2021: Linux namespaces (3): mention that a chroot will happen in addition to mounting things; be more explicit about how user namespaces change things, opting out of sudo, effectively
    \end{itemize}
\end{frame}
}




\begin{frame}{last time}
    \begin{itemize}
    \item Rust options for ``smart pointer'' types
    \item other language enforcement ideas: e.g. constant-time
    \vspace{.5cm}
    \item what programs are allowed to do vs. what programs need
        \begin{itemize}
        \item goal: ``least privilege''
        \end{itemize}
    \item privilege separation as application design
        \begin{itemize}
        \item examples: Chrome, OpenSSH
        \end{itemize}
    \item mechanism: system call filtering
    \item problem: more precise system call filtering?
    \end{itemize}
\end{frame}

\begin{frame}{challenge/final logistics}
    \begin{itemize}
    \item CHALLENGE assignment plan:
        \begin{itemize}
        \item 9\% of final grade (= approx. 2 homeworks)
        \item 7 ``make this program output X'' problems
        \item solve any 5 for full credit
        \item expect to release no later than 30 April
        \item due 12 May 2021 @ 9pm
        \end{itemize}
    \item FINAL quiz
        \begin{itemize}
        \item 6\% of final grade
        \item focused on material that can't be covered by CHALLENGE
        \item intending something that won't take longer than 90 minutes 
            \begin{itemize}
            \item (it varies how good I am meeting that target)
            \end{itemize}
        \item released 12 May 2021 @ 9pm
        \item due 13 May 2021 @ 9pm
        \item (our official final period: 2-5pm 13 May)
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{challenge assistance policy}
    \begin{itemize}
    \item Please do not discuss or expect TAs (or me) to answer questions about what strategy you should apply to particular challenges. You are responsible for figuring this out yourself.
    \item You may, however, ask TAs or share general information about how to identify whether an exploit technique is applicable to a particular program or about how to apply an exploit technique to other executables.
    \vspace{.5cm}
    \item We will supply reference solutions to homework assignments.
    \end{itemize}
\end{frame}

\section{more fine-grained filtering?}
\input{../sandbox/linux-syscall-filter-delta}

% FIXME: without seccomp, ptrace-based filtering

\subsection{applied to VLC?}
\input{../sandbox/app-confine-vlc-example}

\subsection{shared services?}
\input{../sandbox/app-confine-shared-services}

\subsection{pro/con shared services}
\input{../sandbox/app-confine-levels}

\subsection{SELinux}
\input{../sandbox/selinux}

\subsection{versus capability-type approach}
\input{../sandbox/v-cap-approach}

\subsection{chroot}
\input{../sandbox/chroot}

\subsubsection{exercise}
\input{../sandbox/chroot-exer}

\subsection{Linux namespaces}
\input{../sandbox/linux-ns}

% FIXME: Chrome sandboxing failing:
    % https://theori.io/research/escaping-chrome-sandbox/
        % Binder (Chrome internal IPC library)
    % % https://googleprojectzero.blogspot.com/2020/04/you-wont-believe-what-this-one-line.html
    % https://bugs.chromium.org/p/project-zero/issues/detail?id=1991
    % https://bugs.chromium.org/p/project-zero/issues/detail?id=1985

% FIXME: SELinux sandbox escape:
    % https://www.openwall.com/lists/oss-security/2016/09/25/1

\subsection{Linux programs that attempt confinement}
\input{../sandbox/example-linux}

\subsection{containers}
\input{../sandbox/containers}


\subsubsection{runC bug}
\input{../sandbox/runc-bug}
\end{document}
