\date{}
\title{}
\date{}
\usepackage[outputdir=latex.out]{minted}
\begin{document}
\begin{frame}
    \titlepage
\end{frame}

\input{../common/listingsLib}

\begin{frame}{last time}
    \begin{itemize}
    \item some strategies for static analysis
        \begin{itemize}
        \item not running code like symbolic exec/fuzzing/etc.
        \item can use approximations of possible code paths
        \item track abstraction of value\ldots
            \begin{itemize}
            \item things pointer could point to
            \item is pointed-to-value free/not-free at this time
            \end{itemize}
        \end{itemize}
    \item difficulty of sandboxing
        \begin{itemize}
        \item what applications need to do
        \end{itemize}
    \item privilege separation
    \item sandboxing via system call filters
    \end{itemize}
\end{frame}

\begin{frame}{quiz}
\end{frame}

\begin{frame}{assignment Q+A}
\end{frame}

\section{Linux system call filtering}
\subsection{simple Linux system call filtering}
\input{../sandbox/linux-syscall-filter}

\section{aside: strace}
\input{../sandbox/strace-hello}

\subsection{more fine-grained filtering?}
\input{../sandbox/linux-syscall-filter-delta}

\input{../sandbox/linux-syscall-filter-bpf}

\input{../sandbox/linux-syscall-open-filter-hard}

\section{libseccomp}
\input{../sandbox/libseccomp}


\subsection{more sophisticated filters}
\section{Chrome architecture}
\input{../sandbox/chrome-arch}

% FIXME: Chrome Site Isolation
\subsection{Site Isolation}
\input{../sandbox/chrome-site-isolation}

\section{OpenSSH architecture}
\input{../sandbox/openssh-privsep}

\subsection{exercise: priv sep for}
\input{../sandbox/priv-sep-for-exer}

\section{normal application confinement?}
\input{../sandbox/app-confine-intro}


\subsection{applied to VLC?}
\input{../sandbox/app-confine-vlc-example}

\subsection{shared services?}
\input{../sandbox/app-confine-shared-services}

\subsection{pro/con shared services}
\input{../sandbox/app-confine-levels}


\subsection{versus capability-type approach}
\input{../sandbox/v-cap-approach}

\subsection{chroot}
\input{../sandbox/chroot}

\subsubsection{exercise}
\input{../sandbox/chroot-exer}

\subsection{Linux namespaces}
\input{../sandbox/linux-ns}

% FIXME: Chrome sandboxing failing:
    % https://theori.io/research/escaping-chrome-sandbox/
        % Binder (Chrome internal IPC library)
    % % https://googleprojectzero.blogspot.com/2020/04/you-wont-believe-what-this-one-line.html
    % https://bugs.chromium.org/p/project-zero/issues/detail?id=1991
    % https://bugs.chromium.org/p/project-zero/issues/detail?id=1985

% FIXME: SELinux sandbox escape:
    % https://www.openwall.com/lists/oss-security/2016/09/25/1

\subsection{Linux programs that attempt confinement}
\input{../sandbox/example-linux}

\subsection{containers}
\input{../sandbox/containers}


\subsubsection{runC bug}
\input{../sandbox/runc-bug}

\subsection{SELinux sandbox escape}
\input{../sandbox/selinux-escape}
\section{the Android sandbox}
\input{../sandbox/android-sandbox}

% FIXME: Android sandbox

\subsection{OSX sandboxing}
\input{../sandbox/osx-sandbox}
\subsection{Qubes}
\input{../sandbox/qubes}

\section{Which sandboxing?}
\input{../sandbox/which-sandbox-exer}

\section{sandboxing without OS support}
\input{../sandbox/no-os-support}

\subsection{Wasm}
\input{../sandbox/wasm}


\section{sandboxing API: RLBox}
\input{../sandbox/rlbox}

\section{application permissions}
\input{../sandbox/app-perms}

\subsection{UI problems}
\input{../sandbox/app-perm-problems}

\subsection{do request right permissions?}
\againframe<2>{appPermUI}
\input{../sandbox/app-perm-right}

\subsection{do users understand permissions?}
\againframe<3>{appPermUI}
\input{../sandbox/app-perm-users}

\subsection{how to ask for permission?}
\input{../sandbox/app-perm-how}

\subsection{permissions abuse: Cloak and Dagger}
\input{../sandbox/cloak-and-dagger}

\subsection{permissions abuse: information leak}
\input{../sandbox/info-leak-reardon}


\section{backup slides}
\begin{frame}{backup slides}
\end{frame}

\end{document}
